Improving reproducibility of scientific software using Nix/NixOS: A case study on the preCICE ecosystem

### 2024-08-21 paper/paper.tex
chore: migrate to lstlisting so we can diff those

\usepackage{minted}
\usepackage{subfig}

\usepackage{xcolor}

@@

\begin{figure*}
    \normalsize
    \begin{minted}{nix}
{
  # Inputs including nix functions/packages or additional flags
  lib, stdenv, fetchFromGitHub, cmake, dealii,
  # Optional features that users can enable when overriding
  enable3d ? false }:
stdenv.mkDerivation rec {
  pname = "precice-dealii-adapter";
  version = "unstable-2022-09-23"; # could also be a git tag

@@

  # nix' default phases can be overwritten such as:
  installPhase = ''
    # $out contains the final path inside the nix store.
    # The resulting build files are copied into this directory
    mkdir -p $out/bin && cp elasticity $out/bin/elasticity
  '';
}
    \end{minted}
    \caption{Nix code to package the deal.II-preCICE adapter}
    \label{lst:dealii-adapter-nix}
\end{figure*}

>>>>

\usepackage{subfig}

\usepackage{listings}
\usepackage{xcolor}

\definecolor{identifiercolor}{rgb}{0,0,0}
\definecolor{keywordcolor}{HTML}{1a177d}
\definecolor{commentcolor}{HTML}{3d7a7a}
\definecolor{stringcolor}{HTML}{ba2121}
\definecolor{keywordcolor2}{HTML}{870000}
\definecolor{keywordcolor3}{HTML}{008000}
\definecolor{keywordcolor4}{HTML}{666666}
\lstdefinelanguage{Nix}{
  % Anything betweeen $ becomes LaTeX math mode
  mathescape=false,
  % Comments may or not include Latex commands
  texcl=false,
  keywords=[1]{pname,version,src,owner,rev,repo,sha256,nativeBuildInputs,buildInputs,installPhase},
  % Comments delimiters, we do turn this off for the manual
  comment=[l]{\#},
  % Spaces are not displayed as a special character
  showstringspaces=false,
  % String delimiters
  morestring=[b]",
  morestring=[d]'',
  % Size of tabulations
  tabsize=2,
  % Enables ASCII chars 128 to 255
  extendedchars=false,
  % Case sensitivity
  sensitive=true,
  % Automatic breaking of long lines
  breaklines=false,
  % Default style for listings
  basicstyle=\ttfamily,
  % Position of captions is bottom
  captionpos=b,
  % flexible columns
  columns=[l]fixed,
  % Style for (listings') identifiers
  identifierstyle={\ttfamily\color{identifiercolor}},
  % Style for declaration keywords
  keywordstyle=[1]{\ttfamily\color{keywordcolor}},
  % Style for strings
  stringstyle={\ttfamily\color{stringcolor}},
  % Style for comments
  commentstyle={\ttfamily\color{commentcolor}},
  alsoletter={=}
  %moredelim=**[is][\ttfamily\color{red}]{/&}{&/},
  morekeywords=[2]{false},
  keywordstyle=[2]{\ttfamily\color{keywordcolor2}},
  morekeywords=[3]{rec},
  keywordstyle=[3]{\ttfamily\color{keywordcolor3}},
  morekeywords=[4]{=},
  keywordstyle=[4]{\ttfamily\color{keywordcolor4}},
}[keywords,comments,strings]

@@

\begin{figure*}
    \normalsize
    \begin{lstlisting}[language=Nix]
{
  # Inputs including nix functions/packages or additional flags
  lib, stdenv, fetchFromGitHub, cmake, dealii,
  # Optional features that users can enable when overriding
  enable3d ? false
}:
stdenv.mkDerivation rec {
  pname = "precice-dealii-adapter";
  version = "unstable-2022-09-23"; # could also be a git tag

@@

  # nix' default phases can be overwritten such as:
  installPhase = ''
    # $out contains the final path inside the nix store.
    # The resulting build files are copied into this directory
    mkdir -p $out/bin && cp elasticity $out/bin/elasticity
  '';
}
    \end{lstlisting}
    \caption{Nix code to package the deal.II-preCICE adapter}
    \label{lst:dealii-adapter-nix}
\end{figure*}
